---
title: "Compulsory Exercise 3"
author: Martina Hall, Michail Spitieris, Stefanie Muff, Department of Mathematical
  Sciences, NTNU
date: 'Hand out date: April 14, 2020'
output:
  # html_document:
  #   df_print: paged
  #   toc: no
  #   toc_depth: '2'
  pdf_document:
    toc: no
    toc_depth: '2'
subtitle: TMA4268 Statistical Learning V2020
urlcolor: blue
bibliography: refs.bib
---



<!-- rmarkdown::render("RecEx2-sol.Rmd","all",encoding="UTF-8") -->
<!-- rmarkdown::render("RecEx2-sol.Rmd","html_document",encoding="UTF-8") -->
<!-- rmarkdown::render("RecEx2-sol.Rmd","pdf_document",encoding="UTF-8") -->

Last changes: 13.04.2020

---

**The submission deadline is Sunday, 3. May 2020, 23:59h using Blackboard**


```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE,tidy=TRUE,message=FALSE,warning=FALSE,strip.white=TRUE,prompt=FALSE,
                      cache=TRUE, size="scriptsize",fig.width=4, fig.height=3,fig.align = "center")
```


# Introduction

Maximal score is 50 points. You need a score of 25/50 for the exercise to be approved. Your score will make up 50% points of your final grade.


## Supervision

This project replaces the exam that you would have had to complete individually, thus we do not offer supervision as for compulsory 1 and 2. This avoids also that some students get advantages over others.


## Practical issues

* **You work alone on this project.** 
* **Your submitted pdf MUST NOT HAVE MORE THAN 14 pages! This is a requirement.** Any additional pages **will not be corrected**. Please only report the things that we ask for. For example, for single/multiple choice questions, only report the answers, as we do not grade your explanations in these cases. 
* Remember to write your name on top of your submission.
* The exercise should be handed in as **one R Markdown file and a pdf-compiled version** of the R Markdown file (if you are not able to produce a pdf-file directly please make an html-file, open it in your browser and save as pdf - no, not landscape - but portrait please). We will read the pdf-file and use the Rmd file in case we need to check details in your submission.
* Please do not include all the text from this file (that you are reading now) - we want your R code, plots and written solutions - use the same template as for compulsory 1 (https://wiki.math.ntnu.no/tma4268/2020v/subpage6).
* Please save us time and do NOT submit word or zip, and do not submit only the Rmd. This only results in extra work for us!

## R packages

You need to install the following packages in R to run the code in this file.


```{r,eval=FALSE,echo=TRUE}
install.packages("knitr") #probably already installed
install.packages("rmarkdown") #probably already installed
install.packages("ggplot2") #plotting with ggplot
install.packages("ISLR")
intall.packages("boot")
install.packages("MASS")
install.packages("FactoMineR",dependencies = TRUE)
install.packages("factoextra")
install.packages("ggfortify")
install.packages("glmnet")
install.packages("tree")
install.packages("randomForest")
install.packages("gbm")
install.packages("ggfortify")
install.packages("keras")
install.packages("pls")
install.packages("gam")
```
